Named Entity Recognition on HTML as a web data extraction subtask

### 2018-10-29 tex/article.tex
models

\author{Berthier Ribeiro-Neto}
\affiliation{%
  \institution{Universidade Federal de Minas Gerais}
  \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
  \city{Belo Horizonte}
  \state{MG}
  \postcode{31270-901}
  \country{Brazil}}
\email{berthier.dcc.ufmg@gmail.com}

@@

Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (LSTM-CRF) on the output to tackle
the sequence tagging problem. The CRF layer jointly decodes labels for the whole sentence instead
of predicting each label individually. This architecture achieved an F1 score of 90.10 on the English
data from the ConLL-2003 NER shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
In our experiments, the LSTM-CRF architecture uses a bidirectional LSTM with 100 
hidden states, no peepholes and an input and output dropout layers with a dropout
rate of 0.5. The dropout layers have proven to be very important to prevent overfitting 
and allow better generalization.

@@

Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural network (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
layer is described visually in Figure \ref{fig:cnn}, it receives
only character embeddings as inputs. The character representations generated by the CNN 
are combined with word level representations and then fed to the Bidirectional LSTM with
a CRF output layer described in section \ref{sssec:lstm_crf}.
This architecture can learn morphological features that are very
useful in the NER task, since similar named entities often present morphological similarities. 
This architecture obtained an F1 score of 91.21 in the ConLL2003 dataset. In our experiments, 
the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
neural network with 30 filters and a window size of three characters on top of the LSTM-CRF architecture.
The character embeddings fed to the CNN have 30 dimensions that were randomly initialized.

@@

Lample et al \cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
LSTM representations to form the character representation, as described in figure \ref{fig:lstm_char}. 
This character representation is also combined with a word representation and fed to a LSTM-CRF network. 
The forward LSTM is expected to be a better
representation of the suffix of a token, and the backward LSTM is expected to be a
better representation of the prefix of a token. This differentiates the architecture
from the CNN based approach described in Section \ref{sssec:lstm_crf_cnn}, because CNN filters 
discover positional invariant features, while LSTMs can better represent suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character representations was implemented with a bidirectional LSTM
with 25 hidden states, producing character representations of size 50. The character embeddings
have 30 dimensions that were randomly initialized.

@@

The neural models were trained with mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
parameters, considering the F1 measure in the validation set. All neural models used 
GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training,
they have a vocabulary size of 400.000 words.
In the case of NER on HTML, word embeddings work similar to a gazetteer. Named entities 
of a same type have similar embeddings, so good word embeddings can achieve exceptional 
performance with little training and without a gazetteer.

@@

We collected 145 computer science faculty pages from 42 different countries in
multiple languages, although the English version was prefered when it was available.
We gathered faculty web pages randomly in proportion to
the number of universities in each country\footnote{A detailed list of universities can
be found in https://univ.cc/world.php}. Each HTML page was preprocessed and converted
to the CONLL 2003 data format. That is, one word per line with empty lines representing
sentence boundaries. Sentence boundaries were determined by line break HTML tags
(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). 
Sentences that were more than 50 tokens were also split according to punctuation.

A proper HTML segmenter poses many challenges by itself.
However, we wanted to evaluate models without relying on any sophisticated data record
segmentation system. In many cases, entity annotation may precede the segmentation
phase in web data extraction methods, so annotators have to be able to work with
raw HTML data. Because of the type of documents present in the dataset, many sentences 
contained only one or two tokens, while other documents contained long texts.
Finally, all tokens were tagged using the IOB scheme put forward by
Ramshaw and Marcus \cite{Ramshaw1999}.

@@

The dataset was divided in a training, validation and test set. Table \ref{tab:dataset} contains
a description of the data files. The validation set was used in the early stopping validation strategy
for the neural netowrks and CRF training, while the performance was evaluated by comparing results in the test set.

@@

\subsection{Experiment 2: reduced dataset}

>>>>

\author{Berthier Ribeiro-Neto}
\affiliation{%
  \institution{Universidade Federal de Minas Gerais}
  \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
  \city{Belo Horizonte}
  \state{MG}
  \postcode{31270-901}
  \country{Brazil}}
\email{berthier@dcc.ufmg.br}
\email{berthier@google.com}

@@

Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (LSTM-CRF) on the output to tackle
the sequence tagging problem. The CRF layer jointly decodes labels for the whole sentence instead
of predicting each label individually. This architecture achieved an F1 score of 90.10 on the English
data from the ConLL-2003 NER shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
In our experiments, the LSTM-CRF architecture uses a bidirectional LSTM with 100 
hidden states, no peepholes and input and output dropout layers with a dropout
rate of 0.5. The dropout layers have proven to be very important to prevent overfitting 
and allow better generalization.

@@

Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural network (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
layer is described visually in Figure \ref{fig:cnn}, it receives
only character embeddings as inputs. The character representations generated by the CNN 
are combined with word level representations and then fed to the Bidirectional LSTM with
a CRF output layer described in section \ref{sssec:lstm_crf}.
This architecture can learn morphological features that are very
useful in the NER task, since similar named entities often present morphological similarities. 
This architecture obtained an F1 score of 91.21 in the ConLL2003 dataset. In our experiments, 
the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
neural network with 30 filters and a window size of three characters on top of the LSTM-CRF architecture.
The character embeddings fed to the CNN have 30 dimensions that are randomly initialized.

@@

Lample et al \cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
LSTM representations to form the character representation, as described in figure \ref{fig:lstm_char}. 
This character representation is also combined with a word representation and fed to a LSTM-CRF network. 
The forward LSTM is expected to be a better
representation of the suffix of a token, and the backward LSTM is expected to be a
better representation of the prefix of a token. This differentiates the architecture
from the CNN based approach described in Section \ref{sssec:lstm_crf_cnn}, because CNN filters 
discover positional invariant features, while LSTMs can better represent suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character representations was implemented with a bidirectional LSTM
with 25 hidden states, producing character representations of size 50. The character embeddings
have 30 dimensions that are randomly initialized.

@@

The neural models were trained with mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
parameters, considering the F1 measure in the validation set. All neural models used 
GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training,
they have a vocabulary size of 400.000 words.
In the case of NER on HTML, word embeddings work similar to a gazetteer. Named entities 
with the same type have similar embeddings, so good word embeddings can achieve exceptional 
performance with little training and without a gazetteer.

@@

We collected 145 computer science faculty pages from 42 different countries in
multiple languages, although the English version was prefered when it was available.
We gathered faculty web pages randomly in proportion to
the number of universities in each country\footnote{A detailed list of universities can
be found in https://univ.cc/world.php}. Each HTML page was preprocessed and converted
to the CONLL 2003 data format. That is, one word per line with empty lines representing
sentence boundaries. Sentence boundaries were determined by line break HTML tags
(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). 
Sentences that were more than fifty tokens long were also split according to punctuation.

A proper HTML segmenter poses many challenges by itself.
However, we wanted to evaluate models without relying on any sophisticated data record
segmentation system. In many cases, entity annotation may precede the segmentation
phase in web data extraction methods, so annotators should be able to work with
raw HTML data. Because of the type of documents present in the dataset, many sentences 
contained only one or two tokens, while other documents contained long texts.
Finally, all tokens were tagged using the IOB scheme put forward by
Ramshaw and Marcus \cite{Ramshaw1999}.

@@

The dataset was divided in a training, validation and test set. Table \ref{tab:dataset} contains
a description of the data files. The validation set was used in the early stopping validation strategy
for the neural networks and CRF training, while the performance was evaluated by comparing results in the test set.

@@

\subsection{Experiment 2: Reduced Dataset}
